### 2014-01-15 src/paper.Rnw
update

However, our previous research\cite{icse} suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.

@@

\section{Related Work}
Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager. This was taken up by Offut et al.\cite{offutt1993experimental}. (Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation. However, that paper does not propose it at all. It says we are experimenting with an idea, and that is it. It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness. $\ddot\smile$ - time travel?). The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely. They propose N-selective mutation which avoids N most fertile mutagens. Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation. According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded. He finds that there is no evidence to suggest one over the other. Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation. He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator. He further posits that the mutagens with greatest strength may be the most useful ones. %(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)

>>>>

However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.

@@

\section{Related Work}
Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager. This was taken up by Offut et al.\cite{offutt1993experimental}. (Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation. However, that paper does not propose it at all. It says we are experimenting with an idea, and that is it. It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness. $\ddot\smile$ - time travel?). The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely. They propose N-selective mutation which avoids N most fertile mutagens. Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation. According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded. He finds that there is no evidence to suggest one over the other. Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation. He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator. He further posits that the mutagens with greatest strength may be the most useful ones. %(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
This is taken up later by Mresa\cite{mresa1999efficiency} et al. who used the cost of detection of mutants as a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi). They also find that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, and conversely for less stringent scores, operator selection would be better if const of mutant is considered.

Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting mutagens.

Namin et al.\cite{namin2006finding,siami2008sufficient} treats the operator selection as a variable reduction problem, and applying statistical approaches, finds 28 operators from a total of 108 operators that are sufficient for an adequate test suite.
